\documentclass{beamer}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%Information to be included in the title page:
\title[About Beamer] %optional
{About the Beamer class in presentation making}

\subtitle{A short story}

\author[Arthur, Doe] % (optional, for multiple authors)
{A.~B.~Arthur\inst{1} \and J.~Doe\inst{2}}

\institute[VFU] % (optional)
{
  \inst{1}%
  Faculty of Physics\\
  Very Famous University
  \and
  \inst{2}%
  Faculty of Chemistry\\
  Very Famous University
}

\date[VLC 2013] % (optional)
{Very Large Conference, April 2013}

% \usefonttheme{structuresmallcapsserif} % themes are: structurebold, structurebolditalic, structuresmallcapsserif, structureitalicsserif, serif and default
\usepackage{bookman} % mathptmx, helvet, avat, bookman, chancery, charter, culer, mathtime, mathptm, newcent, palatino, pifont and utopia
\usetheme{Madrid}
\usecolortheme{beaver}

\begin{document}

  \frame{\titlepage}

  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents
  \end{frame}

  \begin{frame}
    \frametitle{Sample frame title}
    This is a text in the first frame. This is a text in the first frame. This is a text in the first frame.
  \end{frame}

  \begin{frame}
    \frametitle{Sample frame title}
    This is a text in second frame.
    For the sake of showing an example.

    \begin{itemize}
     \item<1-> Text visible on slide 1
     \item<2-> Text visible on slide 2
     \item<3> Text visible on slide 3
     \item<4-> Text visible on slide 4
    \end{itemize}

  \end{frame}

  \begin{frame}
    In this slide \pause

    the text will be partially visible \pause

    And finally everything will be there
  \end{frame}

  \begin{frame}
    \frametitle{Sample frame title}

    In this slide, some important text will be
    \alert{highlighted} because it's important.
    Please, don't abuse it.

    \begin{block}{Remark}
      Sample text
    \end{block}

    \begin{alertblock}{Important theorem}
      Sample text in red box
    \end{alertblock}

    \begin{examples}
      Sample text in green box. The title of the block is ``Examples".
    \end{examples}
  \end{frame}

  \begin{frame}
    \frametitle{Two-column slide}

    \begin{columns}
      \column{0.5\textwidth}
        This is a text in first column.
        $$E=mc^2$$
        \begin{itemize}
          \item First item
          \item Second item
        \end{itemize}

      \column{0.5\textwidth}
        This text will be in the second column
        and on a second tought this is a nice looking
        layout in some cases.
    \end{columns}
  \end{frame}
\end{document}
